Effects of the body force on the evacuation dynamics

### 2019-11-26 paper.tex
agregue el diagrama fundamental

@@

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k0.eps}\label{size_distribution_w22_density4.5}}\ 
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k120000.eps}\label{size_distribution_w22_density4.5_kx10}}\\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k0.eps}\label{size_distribution_w22_density5}}\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k120000.eps}\label{size_distribution_w22_density5_kx10}}\\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k0.eps}\label{size_distribution_w22_density5_5}}\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k120000.eps}\label{size_distribution_w22_density5_5_kx10}}
\caption[width=0.47\columnwidth]{}
\label{compresion_distribution}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}
